---
title: "Khaudum Covariates"
author: 'Lindesay Scott-Hayward'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## Load Covariate and point data

```{r}
library(rgdal)
library(rgeos)
library(sp)
require(ggplot2)

path<-'C:/Users/drago/Documents/R Projects/Disso'
```

+ read in the ele and roan data

```{r}
eles<-read.csv(paste('elemydatuse.csv', sep=''))
roan<-read.csv(paste('roanmydatuse.csv', sep=''))
```


+ read in the prediction grid

```{r}
grid_shape<-readOGR(paste(path, '/Khaudum_shapefiles', sep=''), layer='Khaudum_predgrid500m')
predgrid<-grid_shape@data
```

+ read in fire grid

```{r}
fire<-read.csv(paste(path, '/Shapefiles/Fire_500m_grid.csv', sep=''))
```


+ read in the covariate shapefile

```{r}
covar_shape<-readOGR(dsn = paste(path,  '/covariate shape files', sep=''), layer = 'covariates_grid_ref')
```

+ Extract variable data and coordinates

```{r}
covardat<-covar_shape@data
covardat<-data.frame(covardat, coordinates(covar_shape))
```

+ convert lats/longs to UTMs

```{r}
xy <- data.frame(ID = 1:nrow(covardat), X = covardat$coords.x1, Y = covardat$coords.x2)
coordinates(xy) <- c("X", "Y")
proj4string(xy) <- CRS("+proj=longlat +datum=WGS84")  ## for example
res <- spTransform(xy, CRS("+init=epsg:32733"))
covardat$x.pos<- res@coords[,1]
covardat$y.pos<- res@coords[,2]
covardat$area<-0.25
```


## Plot the Variables

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=slope), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('Slope')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=prec_seaso), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('prec_season')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=dry_temp), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('dry_temp')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=IVC_nam), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('IVC_nam')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=et_temp), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('et_temp')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=therm_nam), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('therm_nam')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=forest_occ), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('forest_occ')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=aridity), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('aridity')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=tmean_7), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('tmean_7')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=temp_an_ra), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('temp_an_ra')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=isothermal), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('isothermal')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=lith_nam), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('lith_nam')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=max_temp_w), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('max_temp_w')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=growth_per), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('growth_per')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=river_dist ), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('river_dist ')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=temp_seaso), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('temp_seaso')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=altitude), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('altitude')
```

```{r, dev='png'}
ggplot(covardat) + 
  geom_tile(aes(x.pos/1000, y.pos/1000, fill=waterpoint), height=0.5, width=0.5) +
  theme_bw() + xlab('Easting (Km)') + ylab('Northing (Km)') +
  coord_equal() +
  ggtitle('waterpoint')
```


Two variables are constant across the dataset:
veg_type, rainmonths

## Example of interpolating variables for the ele/roan tag data locations

Testing using the waterpoint variable from the covariate shape file.  This seems to conflict with the waterpoint information give in the shapefile provided by Piet. 

```{r}
eles$testwaters<-akima::interpp(covardat$x.pos, covardat$y.pos, 
                                covardat$waterpoint, 
                                eles$x.pos, eles$y.pos, duplicate="mean")$z
```

```{r}
require(fields)
par(mfrow=c(1,2))
quilt.plot(eles$x.pos, eles$y.pos, eles$mindistToWaters, asp=1, nrow=53, ncol=87, main='Piet Points')
quilt.plot(eles$x.pos, eles$y.pos, eles$testwaters, asp=1, nrow=53, ncol=87, main='Morgan Data')
```

